A Methodology to Define QoS and SLA Requirements in Service Choreographies

### 2012-08-02 articles/CAMAD2102/article-version2.tex
Formatting significant digits and correcting correcting inconsistencies

\begin{table}[!h]
    \centering
    \caption{Results  (in \%) }
    \label{table:simulationsAll}
    \begin{tabular}{|l|l|l|l|l|}
	  \hline
		       & \multicolumn{2}{c|}{ Average number of tokens } & \multicolumn{2}{c|}{ 95\% Confidence interval  (+/-) }\\
	  \hline
	  Place      &  Scenario 1   &   Scenario 2  	 &  Scenario 1 	  &   Scenario 2 \\
	  \hline
	  $Start$ &    35,277	 &    40,14833        &   5,83475    	 &    6,23113         \\
	  $End$   &    41,94523	 &    38,78167        &   2,53329  	  &  3,82088	\\
	  $A_1$   &    0,07825	 &    0,08333         &   0,00105   	&  0,00369     \\ %% após da execucao do Treceive 1
	  $B_2$	  &    0,03599	&     0,00469 		& 	0,00604 &  0,00651 \\ %% após da execucao do Treceive 2
	  $B_3$	  &    0,03991	&     0,0099  		& 0,00643 	&  0,00742 \\ %% após da execucao do Treceive 3
      \hline
	  $B_1$	  &    0,07668	 &  3,22932  		& 0,00056	&  0,00168	\\ %Primeiro participante em iniciar a interação
	  $A_2$	  &    0,03599	 &  0,00843		& 0,00643	&  0,00724	\\ %% aceito
	  $A_3$	  &    0,04069	 &  0,00531		& 0,00612	&  0,00638	\\ %%rejeitado
        \hline
	  $M_{err1}$	& 0,39202	&     0,90583 		& 0,94914	&  1,92248	\\
	  $M_{err2}$	& 0	 &    0,9325 		& 0,62632		&  0,63929	\\
	  $M_{err3}$	& 0   & 0,65583 		& 0,86536	&  0,74018	\\
        \hline
	  $C_{err1}$	& 0,73787 	 & 2,93833 	& 0,81703	&  2,02391	\\
	  $C_{err2}$	& 0	         & 0 		& 0,66667	&  1,75059	\\
	  $C_{err3}$ 	& 0,77856	 & 0.16233 	& 0,91667	&  1,51997	\\
        \hline
	  $C_{i1}$ 	& 8,32316	 & 8,90167 	& 5,32508	&  7,47872	\\
      $C_{i2}$ 	& 0,62676	 & 0,6875 	& 0,22787	&  0,52219	\\
      $C_{i3}$ 	& 0,75039	 & 8,90167 	& 0,39	&  0,21236	\\

@@

By the results presented in Table~\ref{table:simulationsAll} it is possible to note that in the Scenario 1, an average of $1.51643\%$ ($Cerr1 + Cerr2 + Cerr3$) of 
the instances didn't  finish the process because of error in the network in the moment of the message exchanges. Also, an average
 of $0,39202\%$ ($Merr1 + Merr2 + Merr3$) of the instances didn't finish the process because of error in the messages
 format, detected when the messages were received.

%Da mesma forma, no cenário $2$  houve uma perda de   $4,52167\%$ ($Cerr1 + Cerr2 + Cerr3$) e   $2,49416\%$ ($Merr1 + Merr2 + Merr3$)  de instâncias que não terminaram o processo por causa de erros de comunicação e de formato de mensagem respectivamente. Resultando que efetivamente houve uma maior perda de instâncias de coreografias do que no cenário $1$. No entanto, o que se manteve foi  o gargalo achado no começo da comunicação na primeira interação ($C_{i1}$), retendo  em média $8,32316\%$ e $8,90167\%$ das instâncias antes de serem enviadas pela rede o que pode contribuir em um atraso do tempo de execução total do processo.
Similarly to the Scenario 1, in Scenario 2 $4,52167\%$ and $2,49416\%$ of the instances didn't finish the process because of error in 
the network and in the message format respectively. As expected, the results are inline with the parameters
 defined to each scenario (Table~\ref{table:transitionsConfigurations}).

One important finding with the simulation of these scenarios, and that can be useful to developers and network administrators is related with the existing 
bottleneck in the first iteration ($C_{i1}$), which avoided $8,32316\%$ and $8,90167\%$ of the instances for being send via
 network. This information can affect the implementation of the definite choreography or even define new QoS policies to be
 configured in the network to reduce the delay of the executions.

>>>>

\begin{table}[!h]
    \centering
    \caption{Results  (in \%) }
    \label{table:simulationsAll}
    \begin{tabular}{|l|l|l|l|l|}
	  \hline
		       & \multicolumn{2}{c|}{ Average number of tokens } & \multicolumn{2}{c|}{ 95\% Confidence interval  (+/-) }\\
	  \hline
	  Place      &  Scenario 1   &   Scenario 2  	 &  Scenario 1 	  &   Scenario 2 \\
	  \hline
	  $Start$ &    35,28	 &    40,15        &   5,83    	 &    6,23         \\
	  $End$   &    41,95	 &    38,78        &   2,53  	  &  3,82	\\
	  $A_1$   &    0,08	 &    0,08         &   0,00   	&  0,00     \\ %% após da execucao do Treceive 1
	  $B_2$	  &    0,04	&     0,01 		& 	0,01 &  0,01 \\ %% após da execucao do Treceive 2
	  $B_3$	  &    0,04	&     0,01  		& 0,01 	&  0,01 \\ %% após da execucao do Treceive 3
      \hline
	  $B_1$	  &    0,08	 &  3,23  		& 0,00	&  0,00	\\ %Primeiro participante em iniciar a interação
	  $A_2$	  &    0,04	 &  0,01		& 0,01	&  0,01	\\ %% aceito
	  $A_3$	  &    0,04	 &  0,01		& 0,01	&  0,01	\\ %%rejeitado
        \hline
	  $M_{err1}$	& 0,39	 & 0,91 		& 0,95	&  1,92	\\
	  $M_{err2}$	& 0,00	 & 0,93 		& 0,63		&  0,64	\\
	  $M_{err3}$	& 0,00   & 0,66 		& 0,87	&  0,74	\\
        \hline
	  $C_{err1}$	& 0,74 	 & 2,94 	& 0,82	&  2,02	\\
	  $C_{err2}$	& 0,00	 & 0,00 	& 0,67	&  1,75	\\
	  $C_{err3}$ 	& 0,78	 & 0.16 	& 0,92	&  1,52	\\
        \hline
	  $C_{i1}$ 	& 8,32	 & 8,90 	& 5,33	&  7,48	\\
      $C_{i2}$ 	& 0,63	 & 0,69 	& 0,23	&  0,52	\\
      $C_{i3}$ 	& 0,75	 & 8,90 	& 0,39	&  0,21	\\

@@

By the results presented in Table~\ref{table:simulationsAll} it is possible to note that in the Scenario 1, an average of $1.52\%$ ($C_{err1} + C_{err2} + C_{err3}$) of 
the instances didn't  finish the process because of error in the network in the moment of the message exchanges. Also, an average
 of $0,39\%$ ($M_{err1} + M_{err2} + M_{err3}$) of the instances didn't finish the process because of error in the messages
 format, detected when the messages were received.

%Da mesma forma, no cenário $2$  houve uma perda de   $4,52167\%$ ($Cerr1 + Cerr2 + Cerr3$) e   $2,49416\%$ ($Merr1 + Merr2 + Merr3$)  de instâncias que não terminaram o processo por causa de erros de comunicação e de formato de mensagem respectivamente. Resultando que efetivamente houve uma maior perda de instâncias de coreografias do que no cenário $1$. No entanto, o que se manteve foi  o gargalo achado no começo da comunicação na primeira interação ($C_{i1}$), retendo  em média $8,32316\%$ e $8,90167\%$ das instâncias antes de serem enviadas pela rede o que pode contribuir em um atraso do tempo de execução total do processo.
Similarly to the Scenario 1, in Scenario 2, an average of $3,10\%$ and $2,50\%$ of the instances didn't finish the process because of error in 
the network and in the message format respectively. As expected, the results are inline with the parameters
 defined to each scenario (Table~\ref{table:transitionsConfigurations}).

One important finding with the simulation of these scenarios, and that can be useful to developers and network administrators is related with the existing 
bottleneck in the first iteration ($C_{i1}$), which avoided $8,32\%$ and $8,90\%$ of the instances for being send via
 network. This information can affect the implementation of the definite choreography or even define new QoS policies to be
 configured in the network to reduce the delay of the executions.
